Slavnov products and KP tau functions

### 2025-05-07 draft.tex
finish last section of the paper

Putting all these facts together, we write the Baker-Akhiezer function
as 
\begin{equation}
  \psi(\lambda; \bm{z}, \bm{v}) =
  e^{\xi(\bm{t}, \lambda)}  \left[ 1 + 
  \sum_{p=1}^n (-1)^p \lambda^{-p} \sigma_p^{(n)}(\bm{z}^{-1})
    + \frac{1}{\bm{\tau}(\bm{z}, \bm{v})}
    \det \widehat{\mathcal{K}}_{[\bm{F} \to n-row]}
  \right]\; .
\end{equation}

@@

We finally conclude that the Bakher-Akhiezer function can be written as
\begin{equation}
  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
  \det \left( \mathbb{1} +
    \frac{1}{\lambda} \mathcal{T}
  \right)\; .
\end{equation}
where \(\mathcal{T} = \mathcal{K}^{-1} \check{\mathcal{K}}\).

\subsection{Problems}
Here are some important comments and problems to discuss.

>>>>

Putting all these facts together, we write the Baker-Akhiezer function
as 
\begin{equation}
  \psi(\lambda; \bm{z}, \bm{v}) =
  e^{\xi(\bm{t}, \lambda)}  \left[ 1 + 
  \sum_{p=1}^n (-1)^p \lambda^{-p} \sigma_p^{(n)}(\bm{z}^{-1})
    + \frac{1}{\bm{\tau}(\bm{z}, \bm{v})}
    \det \widehat{\mathcal{K}}_{[\bm{F} \to n-row]}
  \right]\; .
\end{equation}
Next section we find a better expression for the Baker-Akhiezer
function.

@@

We finally conclude that the Bakher-Akhiezer function can be written as
\begin{equation}
  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
  \det \left( \mathbb{1} + 
    \frac{1}{\lambda} \mathcal{M}
  \right)\; , 
\end{equation}
where \(\mathcal{M} = \mathcal{K}^{-1} \check{\mathcal{K}}\) is a
finite dimensional matrix. Let us now use the elementary expression
\begin{subequations}
\begin{equation}
  \begin{split}
    \det \left( \mathbb{1} + \frac{1}{\lambda} \mathcal{M}\right)
    & = \exp \left[ \Tr \log \left( \mathbb{1} + \frac{1}{\lambda} \mathcal{M} \right) \right]\\
    & = \prod_{l=1}^n \left( 1 + \frac{\mu_l}{\lambda} \right) \; ,
  \end{split}
\end{equation}
\end{subequations}
where \(\bm{\mu} = \{\mu_l\}_{l=1}^n\) are the eigenvalues of the
matrix \(\mathcal{M}\), and these obviously depend on the Bethe roots
\(\bm{v}\) and parameters \(\bm{t}\). Therefore, we have
\begin{equation}
  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
  \left(1 + \sum_{k=1}^n \frac{\xi_k(\bm{t})}{\lambda^k} 
  \right)\; . 
\end{equation}
where \(\xi_k(\bm{t}) = \sigma_k^{(n)}(\mu_1, \dots, \mu_n)\) and \(\mu_j = \mu_j(\bm{t}, \bm{v})\).

We can also write 
\begin{equation}
  \begin{split}
    \det \left( \mathbb{1} + \frac{1}{\lambda} \mathcal{M}\right)
    & = \prod_{l=1}^n \left( 1 + \frac{\mu_l}{\lambda} \right) \\ 
  \end{split}
\end{equation}

In the limit \(n \to \infty\) with with \(n/L \to 0\), we have
that the Baker-Akhiezer function can be written as
\begin{equation}
  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
  \left( 1 + \sum_{k=1}^n \frac{(-1)^k}{\lambda^k} \sigma_k(\{\bm{p}\})
  \right)\; . 
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Discussion}
